Wordstack and outline of the manuscript

### 2022-09-20 paper/manuscript.Rmd
Rewrite introduction

# Introduction

## Trends of biodiversity need to be assessed at multiple facets

Multiple studies reported dramatic declines of population and community biomass
[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] but
also recent studies reported non significant temporal trends in species richness
[@vellend_global_2013; @dornelas_assemblage_2014; @blowes_geography_2019], total
abundance [@klink_meta-analysis_2020], high turnover in species composition
[@dornelas_assemblage_2014; @blowes_geography_2019]. Unfortunately, studies
often focus on the temporal trend of one dimension of biodiversity
[@hallmann_more_2017; @klink_meta-analysis_2020, but see 2 in
@dornelas_assemblage_2014; @blowes_geography_2019]. However biodiversity is a
multidimensional concept and the functioning of ecosystem depends ultimately on
several dimensions of biodiversity, such as species richness, evenness and
functional composition^[1]  [@cardinale_biodiversity_2012; @duffy_why_2009], the
documentation of the trend of one biodiversity facet is likely insufficient to
understand changes in community structure and ultimately predict their
consequences on ecosystem functioning.

[^1]: Commentaire de Colin: *je pense qu'il faut lister les facet de biodiv qu'on
va etudier. sans forcement s'y limiter?* Ici je pense que la composition en role
trophique rentre dans "functional composition" sans rentrer dans le détail.

## Current knowledge mainly comes from space-for-time substitution

Current knowledge on the links among the different facets of biodiversity mainly
comes from spatial comparison [@dunne_network_2006;
@soininen_relationship_2012; @grace_integrative_2016; @danet_species_nodate],
which is used to predict how community structure will change in time, under the
assumption of the space-for-time substitution. It supposes a homology between
variations in space and in time, i.e. that spatial sequences correspond
to temporal sequences. This method have raised criticisms
[@damgaard_critique_2019], with studies showing analogous patterns in space and
time [@blois_space_2013] or not [@johnson_testing_2008;
@adler_contrasting_2007]. Spatial turnover of species composition, dispersal
limitation, disturbance and stochastic processes have been hypothesised to be
responsible for the non-compliance of space-for-time substitution
[@adler_contrasting_2007; @blois_space_2013]. The recent increase in the availability
of temporal monitoring of ecological communities makes possible to address
biodiversity trends for multiple facets.

## Temporal variation of food-webs is largely unknown

More dramatic is that the temporal trends of biodiversity generally neglect
species interactions. Although species interactions determine for a large part
community composition, species coexistence and ecosystem functioning
[@chesson_mechanisms_2000; @thebault_food-web_2003; @oconnor_general_2017].
Furthermore, species interactions can imply tremendous secondary extinctions
[@paine_note_1969; @dunne_network_2002]. In food-webs, spatial comparisons in
empirical and theoretical studies generally reported that trophic level
positively scales to community biomass [@wang_biodiversity_2018;
@danet_species_nodate]. Trophic level has also been shown to stabilise the
temporal variation of community biomass [@shanafelt_stability_2018;
@danet_species_nodate]. Connectance, which measures the degree of generalism in
a network, was shown to increase robustness to extinction [@dunne_network_2002].
However, the temporal variation of food-web structure is largely unknown
[@kortsch_disentangling_2021]. Food-web temporal variation are often reported
across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
@kaartinen_high_2012]. Our knowledge on the variability of food-web structure in
time are even more scarce and particularly how those temporal variations are
linked to the temporal variations of other aspects of biodiversity such as
species richness and community biomass. Spatially, connectance has been shown to
be negatively related to species richness in empirical food-webs [reviewed in
@dunne_network_2006]. Connectance has been shown to scale positively or
negatively with community biomass in theoretical models
[@thebault_food-web_2003; @poisot_trophic_2013]. Average trophic level was
previously shown to scale negatively with species richness
[@danet_species_2021].  In order to improve our knowledge on the consequences of
biodiversity trends such as community biomass and species richness, it is thus
crucial to assess how biomass and species richness temporal trends are
associated to temporal trends of food-web structure.

Even how the temporal trends of community biomass are related to temporal
trends of species richness is still questionned in natural settings, especially
in food-webs. Our knowledge on the relationships between food-web structure and
other facets of biodiversity often comes from the comparison of food-web
snapshots along spatial gradient, raising the question of the validity of
space-for-time substitution to infer consequences of species richness and
community biomass variations on food-web structure.

The increasing availability ecological temporal series and the development of
methods to reconstruct food-webs [@bonnaffe_comparison_2021;
@gravel_inferring_2013; @danet_species_nodate] makes possible to assess the
relationships among several biodiversity facets, including food-web structure.
We used the standardized monitoring of fish freshwater communities on the period
1995-2018 over France, documenting the individual size of fishes in
400 sites during ten years or more. We then reconstruct around 4000 food-webs
based on allometric relationships and food diet data. We questionned i) how
temporal trends of food-web structure are  linked to trends of community biomass
and trends in species richness? ii) Are the relationships observed in time the
same as those observed in space, i.e. is the space-for-time substitution valid?

---
## Variations of community biomass and species richness are predicted to affect
community structure #Changes of species richness and community biomass are
indeed
#predicted to affect community structure. The positive link between biodiversity
#and ecosystem functioning in experimental studies predict that loss and
#gain of species richness should respectively result in loss and gain of
#community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
#this relation is not always found in natural settings [@grace_integrative_2016;
#@li_relationship_2018; @maureaud_biodiversityecosystem_2019].
#
#Variations of species richness can also result in variation of evenness, i.e.
#equitability of species abundances or biomasses. Meta-analysis reported that
#higher evenness of abundances is linked to higher plant biomass in grasslands
#and primary productivity in marine ecosystems [@soininen_relationship_2012].
#Furthermore, studies reported that higher evenness plays a role of insurance in
#face of perturbations [@wittebolle_initial_2009]. Indeed, most studies reported
#positive relationship between species richness and evenness, but also neutral
#and negative ones [@soininen_relationship_2012; @ma_species_2005;
#@maureaud_biodiversityecosystem_2019].
## Variations of community biomass and species richness are predicted to affect food-web structure

---

>>>>

# Introduction (564 words)

Global diversity is reported to decline at alarming rates [@]. At local scale,
recent meta-analysis reported a huge variation in species richness temporal
trends across various taxa and ecosystem types[@vellend_global_2013;
@dornelas_assemblage_2014; @blowes_geography_2019], with no net variations in
species richness[@dornelas_assemblage_2014; @blowes_geography_2019].
Futhermore, recent studies founs that temporal changes in species richness are
unrelated to changes in species composition[@dornelas_assemblage_2014;
@blowes_geography_2019], rising the recognition of the multidimensional nature
of biodiversity changes[@hillebrand_biodiversity_2018; @blowes_local_no_date]
and the need for further investigations on how biodiversity changes over time.

Species interactions among species, described as ecological networks, drive for
a large part community composition, species coexistence, and ecosystem
functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
@oconnor_general_2017]. The structure of ecological networks can trigger or
impede perturbation propagations, i.e secondary extinctions[@paine_note_1969;
@dunne_network_2002; @srinivasan_response_2007;
@stouffer_comparmentalization_2011]. Higher connectance, which measures the
degree of generalism in a network, is predicted to increase robustness to
secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
found that higher trophic level was associated to a lower temporal variability
of community biomass in theoretical models and empirical
data[@shanafelt_stability_2018; @danet_species_nodate]. Then, accounting for how
the structure of ecological networks changes over time according to other
biodiversity facets is crucial.

Th availability of ecological networks timeseries is
scarce[@kortsch_disentangling_2021], such as predictions about how the strucure
of ecological networks change according to changes in species richness come from
spatial comparison. Spatially, connectance has been shown to be negatively
related to species richness in small (i.e. below 20 species) empirical food-webs
[reviewed in @dunne_network_2006], which reflects constraints on the number of
realizable species interactions or an increasing proportion of specialists in
more rich foodwebs. Connectance has been shown to scale positively or negatively
with community biomass in theoretical food-webs [@thebault_food-web_2003;
@poisot_trophic_2013] while the average trophic level was previously shown to
scale negatively with species richness [@danet_species_2021].

However, predicting how ecological networks will change in time according to
other biodiversity facets based on spatial comparison of ecological communities
is valid as long as assumption of the space-for-time substitution is valid as
well. Space-for-time substitution supposes a homology between variations in
space and in time, i.e. that spatial sequences correspond to temporal sequences.
This method have raised criticisms [@damgaard_critique_2019], with studies
showing analogous patterns in space and time [@blois_space_2013] or not
[@johnson_testing_2008; @adler_contrasting_2007]. Spatial turnover of species
composition, dispersal limitation, disturbance and stochastic processes have
been hypothesised to be responsible for the non-compliance of space-for-time
substitution [@adler_contrasting_2007; @blois_space_2013].

The increasing availability ecological temporal series and the development of
methods to reconstruct food-webs [@bonnaffe_comparison_2021;
@gravel_inferring_2013; @danet_species_2021] makes possible to overcome
those research gaps. We used a standardized monitoring of fish riverine 
communities on the period 1995-2018 over France, documenting the individual size
of fishes in 400 sites during ten years or more. We restructed around 4000
food-webs based on allometric relationships and food diet data, and then
computed connectance, and average trophic level as well as community biomass and
species richness.

Our primary objective was to assess how the local structure of foodwebs changes
over time according to simultaneous changes in community biomass and species
richness over time. Our second objective was to assess if the relationships
between changes in food-web structure, community biomass and species richness,
are the same over space and over time, i.e. is the space-for-time substitution
valid?  To do so, we first assessed the temporal trends in food-web structure.
We then built structural equation model to assess the relationships among the
temporal trends of the different facets of food-web structure.

### 2022-09-20 paper/wordstack.Rmd
Late update + add range of temporal data in stations
Fix results
New analysis with different subdataset
Update introduction and results
Rewrite introduction

@@

1. community structure are dynamics and affect ecosystem functions 
    1. species interactions ?
    2. biomass or richness

@@

1. Data selection
2. Community biomass and richness 
3. Network reconstruction
4. Statistical analysis

>>>>

# Main messages

- Different assembly processes between biomass and richness
  - 
- Space for time works well for biomass but less for species richness
  - Connectance and average trophic level

@@

1. Global trends of biodiversity
   1. Global declines and threats 
   2. Reported richness and biomass trends
   3. Continue to explore trends in community structure and its consequences

2. Ecological communities are ecological networks
   1. Species interactions matter for ecosystem functioning
   2.  
3. Trends in richness and biomass should result in alteration of ecological
   networks 
   1. Spatial prediction
   2. But space-for-time...

4. Limitations before this study
   1. Low availability of long temporal series 
   1. No reconstruction method
   1.

5. Study objectives

@@

1. Data selection
2. Community biomass and richness 
3. Network reconstruction
4. Temporal trends 
5. Statistical analysis
